---
title: "lb6"
author: "Eunjin Park"
date: "date"
output:
  pdf_document
header-includes:
- \renewcommand*\familydefault{\sfdefault} %% this picks a sans serif font
- \usepackage[T1]{fontenc}
---
```{r setup, echo=F}
knitr::opts_chunk$set(cache = F)
```

**DELETE ANYTHING FROM THIS TEMPLATE BELOW THAT IS NOT PART OF YOUR SOLUTION.**

(0) Instructions for installing tinytex for PDF rendering: [**https://yihui.org/tinytex/**](https://yihui.org/tinytex/)
 
```{r, eval = F}
install.packages('tinytex')
tinytex::install_tinytex()
```

### I.First section

We will begin by analyzing the data using simple linear regression.
(1) PEC that fits a linear regression model for the proportion of vehicles that are electric as function of
the proportion of people who work from home. Create a plot to assess the assumption of normally-distributed
residuals. What do you notice?
```{r}
car = read.csv("C:/Rlab6/electric_WFH.csv")


car_lm = lm(prop_electric ~ prop_WFH, data = car )

layout(matrix(2:1, ncol = 2))
qqnorm(resid(car_lm))
qqline(resid(car_lm))
plot(car_lm, which = 1)
```
-> There are some outliers, so it is hard to say normally distributed completely. 

(2) [4 pts] PEC that fits a different linear model, this time for the log of the proportion of vehicles that are
electric as a function of the proportion of people who work from home. Again check the assumption of
normally-distributed residuals. What do you notice now?
```{r}
log_proportion = log(prop_electric) ~ prop_WFH
fit_log = lm(log_proportion, data = car)

qqnorm(resid(fit_log))
qqline(resid(fit_log))

```
-> Yes ,can confirm normally-distributed residuals.

(3) [4 pts] Make a plot of the residuals from your model fit in (2) as a function of the fitted values (hint:
plot(..., which = 1) ). What does your plot suggest about the validity of the assumptions of independent
residuals and/or a true linear relationship between the response and predictor?
```{r}
plot(fit_log, which = 1)
```
-> The residuals are mostly negative when the fitted value is small, positive when the fitted value is in the middle and negative when the fitted value is large. That is, the spread is approximately constant, but the conditional mean is not.

(4) [4 pts] Make a plot of the log of the proportion of vehicles that are electric as a function of the proportion
of people who work from home. Add a line that represents the fit from your model in (2) (hint: you might
find the function abline() useful). Make a guess about why your plot in (3) looks the way it does.
```{r}
summary(fit_log)
plot(log(prop_electric)~ prop_WFH, data = car)

abline(a = -5.4910, b = 1.0984)
```

(5) [4 pts] What is the proportion of people who work from home in San Diego County? Use your model from (2)
to make a 95% confidence interval for the expected proportion of vehicles for counties with this proportion
of people working from home. Make sure your prediction is for a proportion, not a log-proportion. How
does your interval compare to the observed proportion of vehicles that are electric in San Diego County?
```{r}
pred = predict(fit_log, newdata = data.frame(prop_WFH = 0.465493213), interval = "confidence")
exp(pred)

```


###II.Generalized Additive Model 

(6) Use the mgcv package to fit a Generalized Additive Model (GAM) for the log of the proportion
of vehicles that are electric as a flexible function of the proportion of people who work from home. Use
the default smoothing basis of thin plate regression splines (i.e., bs = "tp") and a basis dimension of 10.
PEC. Make sure your coefficients match mine.
```{r}
library(mgcv)
fit_gam = gam(log(prop_electric) ~ s(prop_WFH, k =10, bs = "tp"), data = car)
gam.check(fit_gam)
#fit$coefficients
```

(7) Make a plot of residuals as a function of fitted values for your GAM in (6). How does it compare
to the plot for the linear model in (3)? What does your new plot suggest about the validity of model
assumptions?
```{r}
plot(resid(fit_gam) ~ prop_WFH, data=car )

```

(8) [4 pts] Make a new 95% CI for the expected proportion of vehicles that are electric in counties with the same proportion of people working from home as in San Diego County using your GAM from (6). How does your interval compare to the one you made in (5)? To the observed proportion of vehicles that are electric in San Diego County?
```{r}
pred = predict(fit_gam, newdata = data.frame(prop_WFH = 0.465493213), se.fit = TRUE)
CI = exp(pred$fit+ qnorm(c(0.025, 0.975))* pred$se.fit )
CI
```


(9) [4 pts] Fit a new GAM for the log proportion of vehicles that are electric using cubic regression splines
instead of thin plate splines and still uses a basis dimension of 10. PEC.
```{r}
library(mgcv)
fitte = gam(log(prop_electric) ~ s(prop_WFH, k =10, bs = "cr"), data = car)
gam.check(fitte)
```

(10) [4 pts] Make a plot of proportion of vehicles that are electric as a function of the proportion of people
who work from home. Add three curves representing the predicted proportion of vehicles that are electric
according to the (1) linear, (2) GAM with thin plate regression splines and (3) GAM with cubic regression
splines.
```{r}


sequence = seq(from = min(car$prop_WFH), to = max(car$prop_WFH), length.out = 1000)
pred_1 =predict(fit_log, newdata = data.frame(prop_WFH = sequence), se.fit = T)
pred_2 =predict(fit_gam, newdata = data.frame(prop_WFH = sequence), se.fit = T)
pred_3 =predict(fitte, newdata = data.frame(prop_WFH = sequence), se.fit = T)
plot(prop_electric ~ prop_WFH, data = car)

lines(sequence, exp(pred_1$fit), lwd = 2, col = 1)
lines(sequence, exp(pred_2$fit), lwd = 2, col = 2)
lines(sequence, exp(pred_3$fit), lwd = 2, col = 3)
```

